VIP-193: Committee-Based POA

### 2020-02-28 article.tex
revision after my vip193 implemetation

%Note that besides the network synchrony, we also assume that messages be transmitted through gossip communication. Hence, if an honest node receives a message, all other honest nodes will receive the same message with a bounded delay. 
\section{Specifications}
\subsection{Notations}
\renewcommand{\arraystretch}{2}
\begin{longtable}{p{3cm} p{10cm}}
    Symbol  & Description \\
    \hline\hline
    $N$ & Total number of nodes \\
    \hline
    $u=1,2,\dots,N$ & node index \\
    \hline
    $H(\cdot)$ & Cryptographic hash function \\
    \hline
    ${\tt SIG}_u(\cdot)$ & Signature of $u$ \\
    \hline
    $\left({\tt PK}_u,{\tt SK}_u\right)$ & Public and private keys generated by $u$ to sign blocks \\
    \hline
    $\rho\left(\cdot\right)$ & Merkle root of the input set\\
    \hline
    $r$ & Consensus round number \\
    \hline
    $l_r=1,2,...,N$ & Leader in round $r$ \\
    \hline
    $s_r$ & Block summary produced by $l_r$ \\
    \hline
    $\tau_r$ & $s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$ \\
    \hline
    $\epsilon$ & Predefined threshold to determine committee membership \\
    \hline
    $d$ & Number of endorsements required to produce a valid block \\
    \hline
    $\Sigma_r$ & Transaction set prepared by $l_r$ \\
    \hline
    $B_{u,r}^*$ & Last block of the canonical chain (trunk) recognized by $u$ in round $r$\\ 
    \hline
    $H_{vrf},\Pi_{vrf},V_{vrf}$ & Functions that compute hash, generate proof and verify proof defined in the VRF scheme, respectively \\
    \hline
    $\left({\tt PK}_u^{vrf},{\tt SK}_u^{vrf}\right)$ & Public and private key pair generated by $u$ for VRF  \\
    \hline
    ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
    \hline
    % $\omega$, $\omega^*$ & Branch and trunk \\
    % \hline
    $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
    \hline
    $b_m$ & Random beacon computed using randomness from the last block of the $m$'th epoch \\
    \hline
\end{longtable}

\subsection{Committee Membership}
\label{sec:committee}
The verifiable random function can be considered a public-key version of keyed cryptographic hash. The hash of a given message can only be computed by the owner of the private key and can be verified by anyone given the public key~{\tt SK} and message~{\tt M}. The scheme defines the following functions:
\begin{itemize}
    \item $\pi\leftarrow\Pi_{vrf}({\tt SK},{\tt M})$ - function that generates VRF proof;
    \item $\{{\tt TRUE}, {\tt FALSE}\}\leftarrow V_{vrf}({\tt SK},{\tt M},\pi)$ - function that verify VRF proof;
    \item $h\leftarrow H_{vrf}({\tt SK},{\tt M})=H(\pi)$ - function that computes the hash.
\end{itemize}

Node~$u$ determines his committee membership by Algorithm~\ref{alg:committee-gen}. Here ${\tt M}_{\,r}$ can be locally computed by each node in a deterministic way and $\epsilon$ a predefined threshold. See Section~\ref{sec:beacon} for details of how to compute ${\tt M}_{\,r}$. Given the VRF proof~$\pi_{u,r}$ and the corresponding public key~${\tt PK}_u^{vrf}$, anyone can verify the membership claimed by $u$ by Algorithm~\ref{alg:committee-valid} below.

\begin{algorithm}[H]
\caption{Procedure for $u$ to determine his committee membership. }
\label{alg:committee-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute ${\tt M}_{\,r}$
    \State Compute $\pi_{u,r} = \Pi_{vrf}({\tt SK}_u^{vrf},{\tt M}_{\,r})$ and $\lambda=H\left(\pi_{u,r}\right)$
    \vspace{1ex}
    \If{$\lambda\leq\epsilon$}
        \State Return $\left({\tt TRUE},\pi_{u,r}\right)$
    \Else 
        \State Return {\tt FALSE}
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

\begin{algorithm}[H]
\caption{Procedure for anyone to validate $u$'s claimed committee membership.}
\label{alg:committee-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute ${\tt M}_{\,r}$
    \vspace{1ex}
    \If{$V_{vrf}({\tt PK}_u^{vrf},\pi_{u,r})={\tt FALSE}$}
        \State Return {\tt FALSE}
    \EndIf
    \vspace{1ex}
    \State $\lambda\leftarrow H(\pi_{u,r})$
    \vspace{1ex}
    \If{$\lambda\leq\epsilon$}
        \State Return {\tt TRUE}
    \Else 
        \State Return {\tt FALSE}
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

\subsection{Block Summary}
At the beginning of round~$r$, leader $l_r$ computes the summary of the new block, $s_r$, and broadcast it for the committee members to endorse the block. Algorithms~\ref{alg:bs-gen} and \ref{alg:bs-valid} shows the computation and validation process of $s_r$, respectively. In Algorithm~\ref{alg:bs-valid}, $B_{u,r}^*$ is the last block of the canonical chain locally recognized by $u$ at the beginning of round~$r$. Lines~6-10 dictate that $l_r$'s view on the canonical chain must be consistent with that of $u$.

\begin{algorithm}[H]
\caption{Procedure for $l_r$ to compute and broadcast $s_r$.}
\label{alg:bs-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Prepares $\Sigma_r$ and computes $\rho\left(\Sigma_r\right)$
    \State Get the last block on the canonical chain, $B_{l_r}^*$ and computer $h_0=H({\tt HEADER}(B_{l_r,r}^*))$
    \State $s_r\leftarrow h_0\,\|\,r\,\|\,\rho\left(\Sigma_r\right)$
    \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r)\right)$
\end{algorithmic}
\end{spacing}
\end{algorithm}

\begin{algorithm}[H]
\caption{Procedure for $u$ to validate $s_r$.}
\label{alg:bs-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute $l_r$
    \If{$s_r$ is not sent from $l_r$}
        \State Return {\tt FALSE}
    \EndIf
    \vspace{1ex}
    \State Verify ${\tt Sig}_{\,l_r}(s_r)$
    \vspace{1ex}
    \State Extract $B_{u,r}^*$ and compute ${\tt HEADER}(B_{u,r}^*)$
    \If{${\tt HEADER}(B_{u,r}^*)\neq{\tt HEADER}(B_{l_r,r}^*)$}
        \State Return {\tt FALSE}
    \EndIf
    \vspace{1ex}
    \State Return {\tt TRUE}
\end{algorithmic}
\end{spacing}
\end{algorithm}

@@

After receiving block summary~$s_r$, if node~$u$ is a committee member, he then executes Algorithm~\ref{alg:endorse-gen} to endorse the block proposed by $l_r$. Here we define $\tau_r=s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$.

\begin{algorithm}[H]
\caption{Procedure for $u$ to endorse a new block.}
\label{alg:endorse-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    \State Broadcast $\Big(u,s_r,{\tt SIG}_u(\tau_r),\pi_{u,r}\Big)$
\end{algorithmic}
\end{spacing}
\end{algorithm}

Once a node receives an endorsement message from $u$, he first verify $s_r$ by Algorithm~\ref{alg:bs-valid} and then validate $u$'s endorsement by Algorithm~\ref{alg:endorse-valid}.

\begin{algorithm}[H]
\caption{Procedure for validating $u$'s endorsement.}
\label{alg:endorse-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify ${\tt SIG}_{u}(\tau_r)$
    \State Verify $u$'s committee membership by Algorithm~\ref{alg:committee-valid}
\end{algorithmic}
\end{spacing}
\end{algorithm}

\subsection{Block}

Algorithm~\ref{alg:block-gen} describes the procedure for leader~$l_r$ to publish a new block in round~$r$.

\begin{algorithm}[H]
\caption{Procedure for $l_r$ to publish a new block.}
\label{alg:block-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute and broadcast $s_r$ by Algorithm~\ref{alg:bs-gen}
    \State Broadcast TX set~$\Sigma_r$
    \State Wait for $d$ valid endorsements and arrange the committee members such that $u_1<u_2<\dots<u_d$
    \State $\Gamma_r\leftarrow{\tt SIG}_{u_1}(\tau_r)\,\|\,{\tt SIG}_{u_2}(\tau_r)\,\|\,\dots\,\|\,{\tt SIG}_{u_d}(\tau_r)$
    \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r),{\tt Sig}_{\,l_r}(\Gamma_r),
    \left\{u_i,{\tt SIG}_{u_i}(\tau_r),\pi_{u_i,r}\right\}_{i=1}^d\right)$
    \State Construct header body~$\Omega$ and broadcast ${\tt Sig}_{\,l_r}(\Omega)$
\end{algorithmic}
\end{spacing}
\end{algorithm}

A block header body $\Omega$ contains the following elements:
\begin{enumerate}
    \item Hash of the parent header $H({\tt HEADER}(B_{l_r,r}^*))$ 
    \item Round number $r$
    \item TX Merkle tree root $\rho\left(\Sigma_r\right)$
    \item Signature ${\tt Sig}_{\,l_r}(s_r)$
    \item Committee member list $\left(u_1<u_2<\dots<u_d\right)$
    \item Merkle tree root of VRF proofs $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
    \item Merkle tree root of signatures $\left\{{\tt SIG}_{u_i}(\tau_r)\right\}_{i=1}^d$
    \item Signature ${\tt Sig}_{\,l_r}(\Gamma_r)$
    % \item Other necessary header elements such as the state root, receipt root, gas limit and etc.
\end{enumerate}

A block consists of a header $\left\{\Omega,{\tt Sig}_{\,l_r}(\Omega)\right\}$ and TX set~$\Sigma_r$. Algorithm~\ref{alg:block-valid} describes how to validate a block generated in round $r$. To prevent a malicious leader to deliberately delay the transmission of block elements to cause inconsistency, honest nodes would accept a new block only if they validated it in the same round.

\begin{algorithm}[H]
\caption{Procedure for validating a block generated in round $r$.}
\label{alg:block-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    \State Verify $\rho\left(\Sigma_r\right)$
    \For{$i=1,2,\dots,d$}
        \State Verify $u_i$'s endorsement by Algorithm~\ref{alg:endorse-valid}
    \EndFor
    \State Construct $\Gamma_r$ and verify ${\tt Sig}_{\,l_r}(\Gamma_r)$
    \State Construct header body~$\Omega$ and verify ${\tt Sig}_{\,l_r}(\Omega)$
    \State Verify $\Sigma_r$ 
\end{algorithmic}
\end{spacing}
\end{algorithm}

Note that we only list the elements related to the committee mechanism for simplicity. Algorithms~\ref{alg:block-gen} and \ref{alg:block-valid} should be adjusted accordingly to accommodate other elements such as the gas limit, state root, receipt root, etc.

@@

@@

In Algorithms~\ref{alg:committee-gen} and \ref{alg:committee-valid}, nodes need to compute common message~${\tt M}_{\,r}$ to determine and validate committee memberships. It is desirable to add certain randomness in the computation such that adversaries only know their committee memberships in a limited number of rounds in future.

@@

\subsection{Optimizing Bandwidth Usage}
A more efficient usage of network bandwidth often results in a higher system throughput. By more efficient, we mean that there is more time to transmit TXs in each round of consensus. To do that, we detach the endorsing process from the block validation process. In particular, committee members can endorse a new block without receiving and validating the complete set of TXs included in the block. See Algorithms~\ref{alg:bs-gen} and \ref{alg:bs-valid} for details. In this way, we would be able to significantly shorten the whole endorsing process and potentially allow more bandwidth used for TX transmission.

Note that TXs will be checked by nodes when validating any newly received block and any invalid TX will cause the block to be discarded even though all the endorsements are valid.

\subsection{Block Reward}
With the committee mechanism in place, the block reward needs to be shared between the leader and committee members. We propose to give half of the total block reward to the leader and the rest equally distributed to the committee members.

>>>>

%Note that besides the network synchrony, we also assume that messages be transmitted through gossip communication. Hence, if an honest node receives a message, all other honest nodes will receive the same message with a bounded delay. 
\section{Specifications}
\subsection{Notations}
\renewcommand{\arraystretch}{2}
\begin{longtable}{p{3cm} p{10cm}}
    Symbol  & Description \\
    \hline\hline
    $N$ & Total number of nodes \\
    \hline
    $u=1,2,\dots,N$ & node index \\
    \hline
    $H(\cdot)$ & Cryptographic hash function \\
    \hline
    ${\tt SIG}_u(\cdot)$ & Signature of $u$ \\
    \hline
    % $\left({\tt PK}_u,{\tt SK}_u\right)$ & Public and private keys generated by $u$ to sign blocks \\
    % \hline
    $\rho\left(\cdot\right)$ & Merkle root of the input set\\
    \hline
    $r$ & Consensus round number \\
    \hline
    $l_r=1,2,...,N$ & Leader in round $r$ \\
    \hline
    $\Sigma_r$ & Transaction set prepared by $l_r$ \\
    \hline
    $s_r$ & Block summary produced by $l_r$ \\
    \hline
    $x_r$ & Tx-set package produced by $l_r$ \\
    \hline
    $e_{u,r}$ & Endorsement produced by $u$ \\
    \hline
    $d$ & Number of endorsements required to produce a valid block \\
    \hline
    $\pi_{u,r}$ & VRF proof produced by $u$ \\
    \hline
    $h_r$ & Block header produced by $l_r$ \\
    \hline
    % $\tau_r$ & $s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$ \\
    % \hline
    % $\epsilon$ & Predefined threshold to determine committee membership \\
    % \hline
    % $B_{u,r}^*$ & Last block of the canonical chain (trunk) recognized by $u$ in round $r$\\ 
    % \hline
    % $H_{vrf},\Pi_{vrf},V_{vrf}$ & Functions that compute hash, generate proof and verify proof defined in the VRF scheme, respectively \\
    % \hline
    % $\left({\tt PK}_u^{vrf},{\tt SK}_u^{vrf}\right)$ & Public and private key pair generated by $u$ for VRF  \\
    % \hline
    % ${\tt M}_{\,r}$ & Common VRF message generated for committee selection \\
    % \hline
    % % $\omega$, $\omega^*$ & Branch and trunk \\
    % % \hline
    % $m$, $L$ & Epoch number and the number of consensus rounds in one epoch \\
    % \hline
    % $b_m$ & Random beacon computed using randomness from the last block of the $m$'th epoch \\
    % \hline
\end{longtable}

\subsection{Producing a New Block}

Algorithm~\ref{alg:block-gen} describes the procedure for leader~$l_r$ to publish a new block in round~$r$. During the process, nodes needs to deal with four types of packages: 
\begin{itemize}
    \item Block summary~$s_r$
    \item Tx-set package~$x_r$
    \item Endorsement~$e_{u,r}$
    \item Block header~$h_r$
\end{itemize}
They will be described in detail in later sections.

\begin{algorithm}[H]
\caption{Procedure for $l_r$ to publish a new block.}
\label{alg:block-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Prepare and broadcast $s_r$
    \State Prepare and broadcast $x_r$ if there is any tx included in the new block
    \State Wait for $d$ valid endorsements 
    %and arrange the committee members such that ${\tt PK}_{u_1}^{vrf}<{\tt PK}_{u_2}^{vrf}<\dots<{\tt PK}_{u_d}^{vrf}$
    % \State $\Gamma_r\leftarrow{\tt SIG}_{u_1}(\tau_r)\,\|\,{\tt SIG}_{u_2}(\tau_r)\,\|\,\dots\,\|\,{\tt SIG}_{u_d}(\tau_r)$
    % \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r),{\tt Sig}_{\,l_r}(\Gamma_r),
    % \left\{{\tt SIG}_{u_i}(\tau_r),\pi_{u_i,r}\right\}_{i=1}^d\right)$
    % \State Construct header body~$\Omega$ and broadcast ${\tt Sig}_{\,l_r}(\Omega)$
    \State Prepare and broadcast $h_r$
\end{algorithmic}
\end{spacing}
\end{algorithm}

\subsection{Block Summary}
At the beginning of round~$r$, leader $l_r$ computes a summary of the proposed new block, $s_r$, and broadcast it for the committee members to endorse. A block summary must include the following information:
\begin{itemize}
    \item Parent header reference
    \item Merkle root of the transactions included in the new block, $\rho(\Sigma_r)$
    \item Round number, $r$
    \item Leader's signature, ${\tt SIG}_{\,l_r}(\bar{s}_r)$ where $\bar{s}_r$ represents the block summary without a signature
\end{itemize}

% Algorithms~\ref{alg:bs-gen} and \ref{alg:bs-valid} shows the computation and validation processes of $s_r$, respectively.

% \begin{algorithm}[H]
% \caption{Procedure for $l_r$ to compute and broadcast $s_r$.}
% \label{alg:bs-gen}
% \begin{spacing}{1.2}
% \begin{algorithmic}[1]
%     \vspace{1ex}
%     \State Prepares $\Sigma_r$ and computes $\rho\left(\Sigma_r\right)$
%     \State Get $B_{l_r}^*$
%     % \State Get the last block on the canonical chain, $B_{l_r}^*$ and computer $h_0=H({\tt HEADER}(B_{l_r,r}^*))$
%     % \State $s_r\leftarrow h_0\,\|\,r\,\|\,\rho\left(\Sigma_r\right)$
%     \State Prepare $s_r$
%     \State Broadcast $\left(s_r,{\tt Sig}_{\,l_r}(s_r)\right)$
% \end{algorithmic}
% \end{spacing}
% \end{algorithm}

Algorithm~\ref{alg:bs-valid} shows how to validate an incoming block summary.

\begin{algorithm}[H]
\caption{Procedure for $u$ to validate $s_r$.}
\label{alg:bs-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify ${\tt Sig}_{\,l_r}(\bar{s}_r)$
    \State Verify that $r$ is the current round
    \State Verify that $l_r$ is the round leader
    \State Verify that the parent block referred by $s_r$ is consistent with the latest block on the canonical chain
\end{algorithmic}
\end{spacing}
\end{algorithm}

\subsection{Tx-Set Package}
After broadcasting $s_r$, leader~$l_r$ needs to prepare and broadcast the tx-set package~$x_r$. A tx-set package must include the following information:
\begin{itemize}
    \item Round number, $r$
    \item Set of txs included in the new block, $\Sigma_r$
    \item Leader's signature, ${\tt SIG}_{\,l_r}(\bar{x}_r)$ where $\bar{x}_r$ represents the tx-set package without a signature
\end{itemize}

Algorithm~\ref{alg:txset-valid} shows how to validate an incoming tx-set package.

\begin{algorithm}[H]
\caption{Procedure for validating $x_r$.}
\label{alg:txset-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify ${\tt SIG}_{\,l_r}(\bar{x}_r)$
    \State Verify that $r$ is the current round
    \State Verify that $l_r$ is the round leader
\end{algorithmic}
\end{spacing}
\end{algorithm}

@@

After receiving and verifying $s_r$, nodes~$u$ that are selected as the committee members need to prepare and broadcast endorsements~$e_{u,r}$. An endorsement~$e_{u,r}$ must include the following information:
\begin{itemize}
    \item Received and verified block summary, $b_r$
    \item VRF proof of $u$'s committee membership, $\pi_{u,r}$
    \item Signature, ${\tt SIG}_{\,l_r}(\bar{e}_{u,r})$ where $\bar{e}_{u,r}$ represents the endorsement without a signature
\end{itemize}

{\color{red} Note that it is assumed that the private key used by $u$ to generate $\pi_{u,r}$ is different from the one that generates $u$'s address. It is also assumed that the corresponding public key that will be used by other nodes to verify VRF proof can be assessed so that it does not needs to be transmitted with $e_{u,r}$.}

% Here we define $\tau_r=s_r\,\|\,{\tt Sig}_{\,l_r}(s_r)$.
% \begin{algorithm}[H]
% \caption{Procedure for $u$ to endorse a new block.}
% \label{alg:endorse-gen}
% \begin{spacing}{1.2}
% \begin{algorithmic}[1]
%     \vspace{1ex}
%     \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
%     \State Broadcast $\Big(u,s_r,{\tt SIG}_u(\tau_r),\pi_{u,r}\Big)$
% \end{algorithmic}
% \end{spacing}
% \end{algorithm}

Algorithm~\ref{alg:endorse-valid} shows how to validate an incoming endorsement by $u$.

\begin{algorithm}[H]
\caption{Procedure for validating $u$'s endorsement.}
\label{alg:endorse-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify ${\tt SIG}_{u}(\tau_r)$
    \State Verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    \State Verify $u$'s committee membership by Algorithm~\ref{alg:committee-valid}
\end{algorithmic}
\end{spacing}
\end{algorithm}

\subsection{Block Header}

After receiving $d$ valid endorsements, leader~$l_r$ needs to prepare and broadcast the header of the new block. A block header~$h_r$ must contain the following information:
\begin{itemize}
    \item Parent header reference 
    \item Round number, $r$
    \item Merkle tree root of the tx set, $\rho\left(\Sigma_r\right)$
    \item Leader's signature on the block summary, ${\tt Sig}_{\,l_r}(s_r)$
    \item VRF proofs of the committee membership from $d$ nodes, $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
    \item Endorsement signatures from the same $d$ nodes, $\left\{{\tt SIG}_{u_i}(\bar{e}_{u,r})\right\}_{i=1}^d$
    \item For any $1\leq i<j\leq N$, $u_i$'s public key for verifying $\pi_{u_i,r}$ should be strictly smaller than that of $u_j$
    \item Leader's signature, ${\tt Sig}_{\,l_r}(\bar{h}_r)$ where $\bar{h}_r$ represents the header without a signature
    % \item Committee member list $\left(u_1<u_2<\dots<u_d\right)$
    % \item Merkle tree root of VRF proofs $\left\{\pi_{u_i,r}\right\}_{i=1}^d$
    % \item Merkle tree root of signatures $\left\{{\tt SIG}_{u_i}(\tau_r)\right\}_{i=1}^d$
    % \item Signature ${\tt Sig}_{\,l_r}(\Gamma_r)$
    % \item Other necessary header elements such as the state root, receipt root, gas limit and etc.
\end{itemize}

% A block consists of a header $\left\{\Omega,{\tt Sig}_{\,l_r}(\Omega)\right\}$ and tx set~$\Sigma_r$. 
Algorithm~\ref{alg:header-valid} describes how to validate a block header generated in round $r$.

%To prevent a malicious leader to deliberately delay the transmission of block elements to cause inconsistency, honest nodes would accept a new block only if they validated it in the same round.

\begin{algorithm}[H]
\caption{Procedure for validating the header of the new block generated in round $r$.}
\label{alg:header-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify ${\tt Sig}_{\,l_r}(\bar{h}_r)$
    \State Verify that $r$ is the current round
    \State Verify that $l_r$ is the round leader
    \State Reconstruct and verify $s_r$ by Algorithm~\ref{alg:bs-valid}
    % \State Verify $\rho\left(\Sigma_r\right)$
    \For{$i=1,2,\dots,d$}
        \If{$i>1$}
            \State Verify that $u_i$'s public key for verifying $\pi_{u_i,r}$ is larger than that of $u_{i-1}$
        \EndIf
        \State Reconstruct and Verify $e_{u_i,r}$ by Algorithm~\ref{alg:endorse-valid}
    \EndFor
    % \State Construct $\Gamma_r$ and verify ${\tt Sig}_{\,l_r}(\Gamma_r)$
    % \State Construct header body~$\Omega$ and verify ${\tt Sig}_{\,l_r}(\Omega)$
    % \State Verify $\Sigma_r$ 
\end{algorithmic}
\end{spacing}
\end{algorithm}

\subsection{Block Assembling}
To use the network bandwidth more efficient, the round leader does not broadcast the whole block, but broadcast the tx-set~$x_r$ and block header~$h_r$ asynchronously. Other nodes need to assemble the new block locally following Algorithm~\ref{alg:block-assembling}.

\begin{algorithm}[H]
\caption{Procedure for verify and assemble the new block generated in round $r$.}
\label{alg:block-assembling}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Verify $h_r$ by Algorithm~\ref{alg:header-valid}
    \State Verify $x_r$ by Algorithm~\ref{alg:txset-valid}
    \State Verify that $\rho(\Sigma_r)$ in $h_r$ is consistent with $x_r$
    \State Verify txs included in $x_r$
    \State Assemble the new block
\end{algorithmic}
\end{spacing}
\end{algorithm}

@@

\subsection{Committee Membership}
\label{sec:committee}
The verifiable random function can be considered a public-key version of keyed cryptographic hash. The hash of a given message can only be computed by the owner of the private key~${\tt SK}$ and can be verified by anyone given the public key~{\tt SK} and message~{\tt M}. The scheme defines the following functions:
\begin{itemize}
    \item $\pi\leftarrow\Pi_{vrf}({\tt SK},{\tt M})$ - function that generates VRF proof;
    \item $\{{\tt TRUE}, {\tt FALSE}\}\leftarrow V_{vrf}({\tt SK},{\tt M},\pi)$ - function that verify VRF proof;
    \item $h\leftarrow H_{vrf}({\tt SK},{\tt M})=H(\pi)$ - function that computes the hash.
\end{itemize}

Node~$u$ determines his committee membership using his private key~${\tt SK}_u$ by Algorithm~\ref{alg:committee-gen}. Here ${\tt M}_{\,r}$ can be locally computed by each node in a deterministic way and $\epsilon$ a predefined threshold. See Section~\ref{sec:beacon} for details of how to compute ${\tt M}_{\,r}$. Given the VRF proof~$\pi_{u,r}$ and the corresponding public key~${\tt PK}_u$, anyone can verify the membership claimed by $u$ by Algorithm~\ref{alg:committee-valid} below.

\begin{algorithm}[H]
\caption{Procedure for $u$ to determine his committee membership. }
\label{alg:committee-gen}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute ${\tt M}_{\,r}$
    \State Compute $\pi_{u,r} = \Pi_{vrf}({\tt SK}_u,{\tt M}_{\,r})$ and $\lambda=H\left(\pi_{u,r}\right)$
    \vspace{1ex}
    \If{$\lambda\leq\epsilon$}
        \State Return $\left({\tt TRUE},\pi_{u,r}\right)$
    \Else 
        \State Return {\tt FALSE}
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

\begin{algorithm}[H]
\caption{Procedure for anyone to validate $u$'s claimed committee membership.}
\label{alg:committee-valid}
\begin{spacing}{1.2}
\begin{algorithmic}[1]
    \vspace{1ex}
    \State Compute ${\tt M}_{\,r}$
    \vspace{1ex}
    \If{$V_{vrf}({\tt PK}_u,\pi_{u,r})={\tt FALSE}$}
        \State Return {\tt FALSE}
    \EndIf
    \vspace{1ex}
    \State $\lambda\leftarrow H(\pi_{u,r})$
    \vspace{1ex}
    \If{$\lambda\leq\epsilon$}
        \State Return {\tt TRUE}
    \Else 
        \State Return {\tt FALSE}
    \EndIf
\end{algorithmic}
\end{spacing}
\end{algorithm}

@@

Nodes need to compute common message~${\tt M}_{\,r}$ to determine and validate committee memberships. It is desirable to add certain randomness in the computation such that adversaries only know their committee memberships in a limited number of rounds in future.

@@

% \subsection{Block Reward}
% With the committee mechanism in place, the block reward needs to be shared between the leader and committee members. We propose to give half of the total block reward to the leader and the rest equally distributed to the committee members.
